---
title: "ADAMidterm"
author: "Mara McKown"
date: '2022-10-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Midterm ADA
### Load packages and open libraries 
```{r, echo=TRUE, message = F}
pacman::p_load(odds.n.ends, blorr, lmtest, car, broom, tidyverse, jtools) 
```

### Question 3
#### a. importing the dataset
```{r}
#import data set from Kim's github account
titanic_data <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")
```

#### b. determining the median age for by passenger class
```{r}
#get some info about the data such as column names, etc.
summary(titanic_data)

#find out what type of class the data is (it is numeric)
class(titanic_data$Pclass) 
#change class to be factorial
titanic_data <- titanic_data %>% 
  mutate(Pclass = factor(Pclass, 1:3)
)
#double check it is now a factor variable
class(titanic_data$Pclass) 

#get summary stats including median age
table1(~ Age | Pclass, data = titanic_data)
```

#### c. a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class
```{r}
#make a boxplot and change theme so it is nicer for me to look at
ggplot() +
  geom_boxplot(data = titanic_data, aes(x = Pclass, y = Age)) +
  theme_bw()
```

#### 4b. Next, add code to determine the percentage of males and females by class. Save this new version and push the new version to your Github repository.
```{r}
# percentage of males and females by class
table1(~ Sex | Pclass, data = titanic_data)
```